### 2025-10-06 thesis/design/functions.tex
Add placeholder algorithms

The following sets are subsequently used to introduce the functions $nq$, $\sigma$, $\phi$, $\pi$, $\rho$ and $\nu$.

@@

@@

@@

@@

@@

The voting function $\nu$ implements a majority voting algorithm similar to that
described by OmniSQL \citep{OmniSQL}, where the result that appears most frequently
across multiple generation attempts is deemed to be the most likely correct answer.
The function applies frequency-based selection among the valid candidates. In cases where
no clear majority exists, the function may apply additional heuristics such as query
complexity or execution performance to determine the final proposed query candidate $w_{consensus}$.

>>>>

The following sets are subsequently used to introduce the functions $\sigma$, $\phi$, $\pi$, $\rho$ and $\nu$.

@@

\begin{algorithm}
\caption{$\sigma$ - Example Selection}\label{algorithms:sigma}
\begin{algorithmic}[1]
%\Require $q \in \mathcal{Q}$, $z \in \Omega_{\mathcal{S}}$, $s \in \mathcal{S}$, $v \in \mathcal{V}$, $d \in \mathcal{D}$
%\Require $k \in \mathbb{N}$, $k \geq 1$             \Comment{Number of examples to select}
%\State $q' \gets mask(q)$                           \Comment{Mask input query}
%\State $z' \gets mask(z)$                           \Comment{Mask zero-shot result}
%\State $candidates \gets \emptyset$                 \Comment{Initialize candidate set}
%\For{each $(q_i, s_i, \omega_i) \in v$}            \Comment{Iterate through embedding space}
    %\State $sim_q \gets cosine(\iota(q'), \iota(mask(q_i)))$  \Comment{Query similarity}
    %\State $sim_s \gets cosine(\iota(z'), \iota(mask(\omega_i)))$  \Comment{SQL similarity}
    %\State $sim_d \gets d(s, s_i)$                  \Comment{Schema distance}
    %\State $score \gets w_q \cdot sim_q + w_s \cdot sim_s + w_d \cdot sim_d$
    %\State $candidates \gets candidates \cup \{(q_i, s_i, \omega_i, score)\}$
%\EndFor
%\State \Return $top\_k(candidates, k)$              \Comment{Return k highest scoring examples}
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\caption{$\phi$ - Schema Subsetting}\label{algorithms:phi}
\begin{algorithmic}[1]
%\Require $c \in \mathcal{C}'$, $s \in \mathcal{S}$
%\State $tables \gets \emptyset$, $columns \gets \emptyset$, $relations \gets \emptyset$
%\For{each $(q_i, s_i, \omega_i, d_i) \in c$}       \Comment{Analyze selected examples}
    %\State $parsed \gets parse\_sql(\omega_i)$      \Comment{Extract schema elements from SQL}
    %\State $tables \gets tables \cup tables(parsed)$
    %\State $columns \gets columns \cup columns(parsed)$
    %\State $relations \gets relations \cup foreign\_keys(parsed)$
%\EndFor
%\State $s' \gets construct\_schema(tables, columns, relations)$  \Comment{Build reduced schema}
%\State \Return $s'$                                 \Comment{Return schema subset}
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\caption{$\pi$ - Query Projection}\label{algorithms:pi}
\begin{algorithmic}[1]
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\caption{$\rho$ - Self Refinement}\label{algorithms:rho}
\begin{algorithmic}[1]
%\Require $q \in \mathcal{Q}$, $s \in \mathcal{S}$, $e \in \mathcal{E}$, $\omega_{raw} \in \Omega_{\mathcal{S}}$
%\Require $max\_attempts \in \mathbb{N}$             \Comment{Maximum refinement attempts}
%\State $\omega_{current} \gets \omega_{raw}$
%\State $attempts \gets 0$
%\While{$attempts < max\_attempts$}
    %\If{$e(\omega_{current}, s)$}                   \Comment{Check if query is valid}
        %\State \Return $\omega_{current}$           \Comment{Return if valid}
    %\EndIf
    %\State $error \gets get\_error(e, \omega_{current}, s)$  \Comment{Extract error details}
    %\State $prompt \gets construct\_refinement\_prompt(q, s, \omega_{current}, error)$
    %\State $\omega_{current} \gets \pi(prompt, s, \emptyset)$  \Comment{Generate refined query}
    %\State $attempts \gets attempts + 1$
%\EndWhile
%\State \Return $\omega_{current}$                   \Comment{Return best attempt}
\end{algorithmic}
\end{algorithm}

@@

The voting function $\nu$ implements a majority voting algorithm similar to that
described by OmniSQL \citep{OmniSQL}, where the result that appears most frequently
across multiple generation attempts is deemed to be the most likely correct answer.
The function applies frequency-based selection among the valid candidates. In cases where
no clear majority exists, the function may apply additional heuristics such as query
complexity or execution performance to determine the final proposed query candidate $\omega_{consensus}$.

\begin{algorithm}
\caption{$\nu$ - Consensus Voting}\label{algorithms:nu}
\begin{algorithmic}[1]
%\Require $C \in \mathcal{C}$, $e \in \mathcal{E}$
%\State $valid\_queries \gets \{\omega \in C : e(\omega, s)\}$  \Comment{Filter valid queries}
%\If{$|valid\_queries| = 0$}
    %\State \Return $null$                           \Comment{No valid candidates}
%\EndIf
%\State $frequency\_map \gets \{\}$                  \Comment{Count query frequencies}
%\For{each $\omega \in valid\_queries$}
    %\State $result \gets execute(\omega, s)$        \Comment{Execute query to get result}
    %\State $frequency\_map[result] \gets frequency\_map[result] + 1$
%\EndFor
%\State $max\_freq \gets max(frequency\_map.values())$
%\State $consensus\_result \gets argmax(frequency\_map, max\_freq)$
%\For{each $\omega \in valid\_queries$}             \Comment{Find query producing consensus result}
    %\If{$execute(\omega, s) = consensus\_result$}
        %\State \Return $\omega$                     \Comment{Return consensus query}
    %\EndIf
%\EndFor
\end{algorithmic}
\end{algorithm}
